MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-02-20 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
rm mean variance plot

# Estimate voom weights with DREAM
tmp = NEW.COUNTS
tmp[is.na(tmp)] = 0
geneExpr = DGEList(tmp)
geneExpr = edgeR::calcNormFactors(geneExpr)

VOOM.GENE_EXPRESSION = variancePartition::voomWithDreamWeights(counts = geneExpr, 
                                                               formula = formula,
                                                               data = COVARIATES)

# Fit linear model using new weights and new design
# CQN NA counts to 0 counts for input to dream()
tmp = CQN.GENE_EXPRESSION$E
tmp[is.na(tmp)] = 0
VOOM.GENE_EXPRESSION$E = tmp
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION, 
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE,
                                        save.plot = TRUE)
plot(VOOM.GENE_EXPRESSION)
violin_plot <- variancePartition::fitExtractVarPartModel(VOOM.GENE_EXPRESSION,
                                                         formula = formula,
                                                         data = COVARIATES)
plotVarPart(sortCols(violin_plot))

>>>>

# Estimate voom weights with DREAM
geneExpr = DGEList(NEW.COUNTS)
geneExpr = edgeR::calcNormFactors(geneExpr)

VOOM.GENE_EXPRESSION = variancePartition::voomWithDreamWeights(counts = geneExpr, 
                                                               formula = formula,
                                                               data = COVARIATES,
                                                               save.plot = TRUE)
#plot(VOOM.GENE_EXPRESSION)

# Fit linear model using new weights and new design
VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION, 
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE)

violin_plot <- variancePartition::fitExtractVarPartModel(VOOM.GENE_EXPRESSION,
                                                         formula = formula,
                                                         data = COVARIATES)
plotVarPart(sortCols(violin_plot))
